Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-21 bdcloud_paper/latex/paper.tex
Added equations for MSM
Added intro paragraph to evaluation

\begin{equation}
Pr(X_{n+1}=x|X_n) = \dots
\end{equation}

@@

\section{Evaluation of the Model}

\textcolor{red}{intro paragraph}

\subsection{Example Analysis of Generated Data}
Using data for 10 stores, 10,000 customers, and five years of transactions generated from the model, we performed two example analyses in support of a fictional advertising campaign. The analyses were designed to be realistic and driven by real-world business concerns.  Due to limited advertising budgets, businesses need to decide who to target and what sort of advertisements are likely to be effective for each type of customer.  We analyzed data generated from the model to determine where the advertising campaigns should be targeted geographically and identify customer purchasing profiles.

>>>>

\textcolor{red}{description. min, max}

\begin{align}
Pr(X_{n+1}&=x|X_n=y) = \\
& \left\{ 
  \begin{array}{l l}
   (1.0 - w_l) W^{-1} \sum_f w_f w_{f,s}(x, y)  & \quad \text{if $x \neq y$}\\
   w_l & \quad \text{if $x = y$}
  \end{array} \right.
\end{align}

\begin{equation}
w_{f,s}(x,y) = \left\{ 
  \begin{array}{l l}
   w_{f,s}  & \quad \text{if $x$.$f$ = $y$.$f$}\\
   1 - w_{f, s} & \quad \text{if $x$.$f$ $\neq$ $y$.$f$}
  \end{array} \right.
\end{equation}

\begin{align}
&w_l \sim N(\mu, \sigma^2) \\
&w_f \sim N(\mu, \sigma^2) \\
&w_{f, s} \sim N(\mu, \sigma^2)
\end{align}

\begin{equation}
W = \sum_i \sum_{j \neq i} \sum_f w_f w_{f,s}(i, j)
\end{equation}

@@

\section{Evaluation of the Model}
In accordance with our original design goals, we evaluated the model and implementation in terms of their abilities to generate semantically-interesting data and scale from a single local machine to a cluster.

\subsection{Example Analysis of Generated Data}
To evaluate the semantic content of the generated data, we performed two example analyses in support of a fictional advertising campaign using data for 10 stores, 10,000 customers, and five years of transactions generated from the model. The analyses were designed to be realistic and driven by real-world business concerns.  Due to limited advertising budgets, businesses need to decide who to target and what sort of advertisements are likely to be effective for each type of customer.  We analyzed data generated from the model to determine where the advertising campaigns should be targeted geographically and identify customer purchasing profiles.
